Extended Abstract: Grounding Language to Reward Functions With Abstract Markov Decision Processes

### 2016-05-10 paper/paper-template-latex/paper_template.tex
Fixed spelling

\section{Introduction}
When dealing with the issue of efficiently solving large-scale sequential decision making problems defined by complex state-action spaces, the ability to identify and leverage multiple layers of abstraction is key. Developing good methods of abstraction represents a logical way to accelerate planning time by breaking apart large, complex tasks into smaller sub-tasks. Moreover, this notion of decomposing tasks into their smaller constituent pieces more closely resembles our own human methodology for solving problems by identifying and completing sub-goals. Our goal in this work is to analyze an alternative method of abstraction for sequential decision making problems that utilizes multiple layers of abstraction over all components of the Markov Decision Process (MDP) in order to efficiently learn in complex domains. In order to convey the strength of the abstraction imposed by the abstract Markov decision process (AMDP) formalism, we extend prior work on grounding natural language commands to reward functions and, in particular, evaluate the succeess of the grounding process as a measure of the strength of the abstraction.

>>>>

\section{Introduction}
When dealing with the issue of efficiently solving large-scale sequential decision making problems defined by complex state-action spaces, the ability to identify and leverage multiple layers of abstraction is key. Developing good methods of abstraction represents a logical way to accelerate planning time by breaking apart large, complex tasks into smaller sub-tasks. Moreover, this notion of decomposing tasks into their smaller constituent pieces more closely resembles our own human methodology for solving problems by identifying and completing sub-goals. Our goal in this work is to analyze an alternative method of abstraction for sequential decision making problems that utilizes multiple layers of abstraction over all components of the Markov Decision Process (MDP) in order to efficiently learn in complex domains. In order to convey the strength of the abstraction imposed by the abstract Markov decision process (AMDP) formalism, we extend prior work on grounding natural language commands to reward functions and, in particular, evaluate the success of the grounding process as a measure of the strength of the abstraction.
